MSPMS-Shiny

### 2024-04-16 mspms_shiny/about.Rmd
more changes

---
title: "MSPMS-Shiny"
author: "Charlie Bayne"
date: "`r Sys.Date()`"
output:
  html_document:
        theme: cosmo
        code_folding: hide
        highlight: tango
        df_print: paged
---

@@

This file should look like the following:

```{r}
DT::datatable(head(mspms::peaks_lfq,2))
```

@@

This file should look like the following:

```{r}
DT::datatable(head(mspms::peaks_id,2))
```

@@

The design matrix file should be a csv file with the following columns: "sample" and "group". The sample column should contain the names of the samples as found in the PEAKS files. The group column should contain the group that the sample belongs to. This can be any thing, as long as it is the same per group.

Here is an example of what the design matrix file should look like for the test files.

```{r}
DT::datatable(mspms::design_matrix)
```

You will also see two tabs at the top of the page, About and Output.. 
About links to these instructions.

@@

>>>>

---
title: "MSPMS-Shiny"
author: "Charlie Bayne"
date: "`r Sys.Date()`"
output:
  html_document:
        theme: cosmo
        highlight: tango
        df_print: paged
---

@@

@@

@@

The design matrix file should be a csv file with the following columns: "sample", "group","condition","time". The sample column should contain the names of the samples as found in the PEAKS files. The group column should contain the group that the sample belongs to. This can be any thing, as long as it is the same per group. The time column should contain the duration of incubation, and the condition column should include any experimental condition such as protease inhibitor.

You will also see four tabs at the side of the page, About, Output, Stats, and DataViz

About links to the instructions shown here

@@

Stats contains a table of the results of the t-tests and ANOVA tests. Be patient, when it is finished the talbe will appear and the data will be ready for download.

DataViz contains a PCA plot, heatmap of the data, and volcano plots of all the data.  Be patient,this takes a while to render.
